---
title: "Untitled"
author: "Anne-Marie Parkinson"
date: "February 22, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

can add usfs and nps boundaries
```{r}
library(tidyverse)
library(janitor)
library(sf) 
library(gganimate)
library(transformr) #need?
library(magick) #need?
library(here)
library(raster) #need?
library(tmap)
library(lubridate)
library(dplyr)
library(lwgeom)
library(ggthemes)


ca_border <-  read_sf(here::here("Arc_data", "ca_state_border"), layer = "CA_State_TIGER2016")
fire <- read_sf(here::here("Arc_data", "fire_perimeter_shpfile"), layer = "fire_perimeters" ) 


fire_animate <- fire %>% 
  clean_names() %>%  
  filter(!is.na(year)) %>% 
  mutate(year = as.numeric(year)) %>% 
  filter(year >= 1936) %>% 
  filter(year <= 1940) %>% 
  st_as_sf() %>% 
  mutate (fire_name = str_to_title(fire_name))  %>% 
  dplyr::filter (acres > 6000)  %>% 
  group_by(year) %>% 
  mutate(cumulative_acres_burned = cumsum(acres)) %>% 
  ungroup(year)
 # st_simplify(dTolerance = 100)  
    
  
ggplot(data = fire_animate) +
    geom_sf(data = ca_border, color = "grey80") +
    geom_sf(data = fire_animate, fill = "red", alpha = 0.8, color = "red") +
    theme_classic() +
    theme_map() +
    labs(title = "Year: {round(frame_time,0)}")  +
    transition_time(year) +
    shadow_mark(alpha = 1)

class(fire)
class(fire$year)
st_crs(fire) #none

```
error for map on first page: 'x' and 'units' must have length > 0 ; 
Error in points[[1]] : subscript out of bounds


#trial 2: use transition states. try to Use year as a factor instead of numeric for this
```{r}
fire_animate <- fire %>% 
  clean_names() %>%  
  filter(!is.na(year)) %>% 
  filter(!is.na(decade)) %>% 
  mutate(year = as.numeric(year)) %>% 
  #filter(year >= 1990) %>% 
  #filter(year <= 1997) %>% 
  filter(year != 1930, 1931, 1985, 1985, 1986, 1998, 1999) %>% 
  st_as_sf() %>% 
  mutate (fire_name = str_to_title(fire_name))  %>% 
  dplyr::filter (acres > 200)  %>% 
  mutate(year = as.numeric(year)) %>% 
   mutate (decade = case_when(
    year < 1900 ~ "1890",
    year < 1909 ~ "1900",
    year < 1919 ~ "1910",
    year < 1929 ~ "1920",
    year < 1939 ~ "1930",
    year < 1949 ~ "1940",
    year < 1959 ~ "1950",
    year < 1969 ~ "1960",
    year < 1979 ~ "1970",
    year < 1989 ~ "1980",
    year < 1999 ~ "1990",
    year < 2009 ~ "2000",
    year < 2019 ~ "2010"
  )) %>% 
  mutate(decade = as.numeric(decade))
  
#year_glue <- str_glue_data(fire_animate2, "Year: {year}")

ggplot(data = fire_animate) +
    geom_sf(data = ca_border, color = "grey80") +
    geom_sf(data = fire_animate, aes(color = decade, fill = decade), alpha = 0.8) +
    theme_classic() +
    theme_map() +
    labs(title = "Year: {round(frame_time,0)}") +
    #labs(subtitle = "Acres Burned: {} ")  +
    transition_time(decade) +
   # transition_states(year) +
    #labs(title = str_glue_data(fire_animate2, "Year: {year}")) +
    ease_aes("linear") +
    shadow_mark(alpha = 0.3)

animate(anim_plot, fps = 10, end_pause = 30)

its just not working. 

```

notes: 
- transtition_states works too when year is a factor. But doesnt like the title changing
- couldn't figure out how to tally acres burned



error: Error in `$<-.data.frame`(`*tmp*`, "id", value = c(1L, 1L, 1L, 1L, 1L,  : 
  replacement has 3568 rows, data has 3562
  
checking to find which years cause error (only for polygons > 200 acres were checked): 
 years >= 2010: okay!
 years 2000 - 2009: okay
 years 1990 - 1999: issue!! so far 1990-97 works
 years 1980 - 1989: issue with polygons <6000 acres (>6000 acres okay); 1980-1985=ok + 1986=issue, exclude 1986 + 1987; 1985-1989=issue,just exclude 1986 85-86=ok. 87-88=ok
 years 1970 - 1979: okay
 years 1960 - 1969: okay!
 years 1950 - 1959: okay!
 years 1940 - 1949: okay!
 years 1930 - 1939: issue!!; 1930-1935=issue, 1936-1939=ok, 1930=ok, 1931=ok; 1932-1939 works!
 years 1920 - 1929: okay!
 years 1910 - 1919: okay!
 years 1900 - 1909: okay!
 years 1880 - 1900: okay!
 
 
 get dubpes (janitor package): is there duplicates of polygons. polygond have the same ID?
 
```{r}
## check polygons 

fire_animate_df <- as.data.frame(fire_animate)
get_dupes(fire_animate_df, geometry)

```
 
 