---
title: "Notes"
author: "Anne-Marie Parkinson"
date: "January 27, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

started off with >21,000 polygons. 

removed some outside of the CA boundary. Removed some that mostly burned in other states. 
removed stands under 10 acres

can look at acres burned/yr
number of fire incidents/yr

large wildfire considered >405ha (1000 acres) by https://agupubs.onlinelibrary.wiley.com/doi/full/10.1002/2014gl059576

sep="" use slider as widget andhave year recognized as a numeric. can use sep="" so there will be no comma in the years

shiny does not like tables made in kable extra!, just user render table

california= 101,676,000 acres

other widgets (shiny idgets package)
```{r}
  numericRangeInput(inputId = "date_fire_causes",
                    label = "Input Year(s)",
                    value = c(unique(fire_causes$year)),
                    separator = "-"),
  
  airYearpickerInput(inputId = "date_fire_causes",
                     label = "Input Year(s)",
                     value = c(unique(fire_causes$year_date)),
                     dateFormat = "yyyy",
                     view = "years",
                     separator = "-",
                     range = T),
multiInput = select multiple values, not a range of values
  
  pickerInput(inputId = "date_fire_causes",
              label = "Input Year(s)",
              choices = c(unique(fire_causes$year_date)),
              multiple = T),
  
```

